Output Summary

### 2021-09-21 03-post-process/output-plots.Rmd
Add a BON to BON survival rate plot

## Smolt-to-Adult Rates

@@

>>>>

## Smolt-to-Adult Rates {.tabset .tabset-pills}

### LGR to Tributary

@@

### BON to BON

```{r bon-to-bon, fig.width = 6, fig.height = 5}
sar_yrs = all_yrs[(jags_data$kmax+1):(jags_data$ny - jags_data$kmax)]

  # summarize rates
  phi_nor = post_summ(post, sub_index("phi_O0_Rb_BON[.+,origin,pop]", origin = o_nor, pop = j))
  phi_hor = post_summ(post, sub_index("phi_O0_Rb_BON[.+,origin,pop]", origin = o_hor, pop = j))

  # get a max value for ylim
  ymax = max(post_summ(post, sub_index("phi_O0_Rb_BON[.+,origin,pop]", origin = o_nor, pop = "."))["97.5%",])

  # make hatchery values NA in year with no smolt
  phi_hor[,zero_hor_smolt] = NA

  # plot natural origin time series
  plot_tseries(est = phi_nor, yrs = sar_yrs, main = pops[j], ylim = c(0, ymax))

  # add hatchery origin time series
  polygon(x = c(sar_yrs, rev(sar_yrs)), y = c(phi_hor["2.5%",], rev(phi_hor["97.5%",])), col = alpha("skyblue2", 0.5), border = NA)
  lines(phi_hor["2.5%",] ~ sar_yrs, col = "blue", lty = 2)
  lines(phi_hor["97.5%",] ~ sar_yrs, col = "blue", lty = 2)
  lines(phi_hor["mean",] ~ sar_yrs, col = "blue", lwd = 2)

  if (j == 1) {
    legend("topright", legend = c("NOR", "HOR"), title = "Origin",
         pch = 22, col = c("red", "blue"), pt.cex = 2, pt.bg = alpha(c("salmon", "skyblue2"), 0.5), bty = "n")
  }
}
par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_fn)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "BON -> BON Survival")
```
